A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2023-08-18 tidyindex.tex
a new section on background to index usage and development + some changes on notation

\usepackage{orcidlink}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data},
  pdfauthor={H. Sherry Zhang; Dianne Cook; Ursula Laa; Nicolas Langrené; Patricia Menéndez},
  pdfkeywords={indexes, data pipeline, software design},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@monash.edu}{\nolinkurl{huize.zhang@monash.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Department of Econometrics and Business
Statistics, Monash University, Melbourne,
Victoria, Australia\\ \textsuperscript{2} Institute of
Statistics, University of Natural Resources and Life
Sciences, Vienna, Austria\\ \textsuperscript{3} Department of
Mathematical Sciences, BNU-HKBU United International College, Zhuhai,
Guangdong, China
\begin{abstract}
Indexes are useful for summarizing multivariate information into single
metrics for monitoring, communicating, and decision-making. While many
work has focused on defining new indexes for the application of
interest, less attention has been directed towards understanding how the
a given index behave under different scenarios. This research introduces
a data pipeline comparising 9 modules to assemble indexes from a series
of modular building blocks. This modular data pipeline is universally
applicable to index computation and allows analysts to incorporate the
analysis on index into the construction pipeline. Analysts can compute
with different index parameters, adjust steps in the index definition by
adding, removing, and swapping them to experiment with various index
designs, calculate uncertainty measures, and assess index robustness .
The paper presents two examples to illustrate the usage of the pipeline.
The first example claculates two drought indexes with different
parameters to investigate the spatio-temporal distribution of drought in
Queensland, Australia. The second example on the Global Gender Gap Index
(GGGI) explores the effects of adjusting linear combination weights on a
country's index values and rankings.
\end{abstract}
\begin{keywords}
\def\sep{;\ }
indexes\sep data pipeline\sep 
software design
\end{keywords}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, sharp corners, enhanced]}{\end{tcolorbox}}\fi

@@

To be able to test different decision choices systematically for an
index, the index needs to be broken down into its fundamental building
blocks to analyze the contribution and effect of each component. We call
this process of breaking the index construction into different steps the
index pipeline. Such decomposition of index components provides the
means to standardize index construction via a pipeline and offers
benefits for comparing among indexes and calculating index uncertainty.
In social indexes, for instance, the OECD handbook (OECD, European
Union, and Joint Research Centre - European Commission 2008) has
provided a set of steps and recommendations for constructing composite
socio-economic indexes. However, there is still a need to extend these
guidelines and methods to accommodate the inclusion of more
methodological complex steps required for indexes in general.

@@

@@

\hypertarget{tbl-notation}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0294}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2206}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1471}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2206}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3824}}@{}}
\caption{\label{tbl-notation}An notation overview of the input,
operation, and output of each pipeline module.}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
No.
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Module
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Input
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Operation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Output
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
No.
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Module
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Input
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Operation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Output
\end{minipage} \\
\midrule()
\endhead
1 & Temporal processing & \(x_{sj}(t)\) & \(f[x_{sj}(t)]\) &
\(x^{\text{Temp}}_{sj}(t^\prime) \quad t^\prime \in D_{t^\prime}\) \\
2 & Spatial processing & \(x_{tj}(s)\) & \(g[x_{tj}(s)]\) &
\(x^{\text{Spat}}_{tj}(s^\prime) \quad s^\prime \in D_{s^\prime}\) \\
3 & Variable transformation & \(x_{j}(s; t)\) & \(T[x_j(s;t)]\) &
\(x^{\text{Trans}}_j(s;t)\) \\
4 & Scaling & \(x_j(s; t)\) & \([x_j(s;t) - \alpha]/\gamma\) &
\(x^{\text{Scale}}_j(s;t)\) \\
5 & Dimension reduction &
\(\mathbf{x}(s;t) \quad \mathbf{x} \subseteq \mathbb{R}^q,\; q\leq p\) &
\(h[\mathbf{x}(s;t)]\) &
\(\mathbf{y}(s;t) \quad \mathbf{y} \subseteq \mathbb{R}^d, d < q\) \\
6 & Distribution fit & \(x_j(s; t)\) & \(F[x_j(s;t)]\) &
\(p_j(s;t) \quad p(.) \in [0, 1]\) \\
7 & Normalising & \(x_j(s; t)\) & \(\Phi^{-1}[x_j(s; t)]\) &
\(z_j(s; t)\) \\
8 & Benchmarking & \(x_j(s; t)\) & \(u[x_j(s;t)]\) & \(b_j(s;t)\) \\
9 & Simplification & \(x_j(s; t)\) & \(v[x_j(s;t)]\) &
\(A_j(s;t) \in \{a_1, a_2, \cdots, a_j\}\) \\
\bottomrule()
\end{longtable}

@@

The temporal processing module takes as input argument a single variable
\(x_{sj}(t)\) at location \(s\) as a function of time. In this step the
original time series can be transformed or summarized into a new one via
time aggregation, the transformation is represented by the function
\(f\), \(x^{\text{Temp}}_{sj}(t^\prime) = f[x_{sj}(t)]\) where
\(t^\prime\) refers to the new temporal resolution after aggregation. An
example of temporal processing done in the computation of the
Standardized Precipitation Index (SPI), consists of summing the monthly
precipitation series over a rolling time window of size \(k\). That is
also known as the time scale. For SPI, the choice of the time scale
\(k\) is used to control the accumulation period for the water deficit,
enabling the assessment of drought severity across various types
(meteorological, agricultural, and hydrological).

@@

Dimension reduction takes the multivariate information
\(\mathbf{x}(s;t)\), where
\(\mathbf{x} \subseteq \mathbb{R}^q,\; q\leq p\), as the input. It
summarises the high-dimensional information into a lower-dimension
representation \(\mathbf{y}(s;t)\), where \(y \subseteq \mathbb{R}^d\)
and \(d < q\), as the output. The transformation can be based on
domain-specific knowledge, originating from theories describing the
underlying physical processes, or guided by statistical methods. For
example, the Standardized Precipitation-Evapotranspiration Index (SPEI)
calculates the difference \(D\) between precipitation (\(P\)) and
potential evapotranspiration (\(\text{PET}\)), using a water balance
model (\(D = P - \text{PET}\)). This is the only step that differs from
the Standardized Precipitation Index (SPI).

@@

The R package \texttt{tidyindex} implements the index pipeline modules
described in Section~\ref{sec-pipeline}. These modules compute an index
in a sequential manner, as shown below:

@@

@@

This work is funded by a Commonwealth Scientific and Industrial Research
Organisation (CSIRO) Data61 Scholarship. The article is created using
Quarto in R. The source code for reproducing this paper can be found at:
https://github.com/huizezhang-sherry/paper-tidyindex.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-buja_elements_1988}{}}%
Buja, A, D Asimov, C Hurley, and JA McDonald. 1988. {``Elements of a
Viewing Pipeline for Data Analysis.''} In \emph{Dynamic Graphics for
Statistics}, 277--308. Wadsworth, Belmont.

@@

@@

@@

@@

>>>>

\usepackage{orcidlink}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data},
  pdfauthor={H. Sherry Zhang; Dianne Cook; Ursula Laa; Nicolas Langrené; Patricia Menéndez},
  pdfkeywords={indexes, data pipeline, software
design, uncertainty, decision-making},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@monash.edu}{\nolinkurl{huize.zhang@monash.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Department of Econometrics and Business
Statistics, Monash University, Melbourne,
Victoria, Australia\\ \textsuperscript{2} Institute of
Statistics, University of Natural Resources and Life
Sciences, Vienna, Austria\\ \textsuperscript{3} Department of
Mathematical Sciences, BNU-HKBU United International College, Zhuhai,
Guangdong, China
\begin{abstract}
Indexes are useful for summarizing multivariate information into single
metrics for monitoring, communicating, and decision-making. While many
work has focused on defining new indexes for the application of
interest, less attention has been directed towards understanding how the
a given index behave under different scenarios. This research introduces
a data pipeline comparising 9 modules to assemble indexes from a series
of modular building blocks. This modular data pipeline is universally
applicable to index computation and allows analysts to incorporate the
analysis on index into the construction pipeline. Analysts can compute
with different index parameters, adjust steps in the index definition by
adding, removing, and swapping them to experiment with various index
designs, calculate uncertainty measures, and assess index robustness .
The paper presents two examples to illustrate the usage of the pipeline.
The first example claculates two drought indexes with different
parameters to investigate the spatio-temporal distribution of drought in
Queensland, Australia. The second example on the Global Gender Gap Index
(GGGI) explores the effects of adjusting linear combination weights on a
country's index values and rankings.
\end{abstract}
\begin{keywords}
\def\sep{;\ }
indexes\sep data pipeline\sep software design\sep uncertainty\sep 
decision-making
\end{keywords}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, boxrule=0pt, sharp corners, breakable]}{\end{tcolorbox}}\fi

@@

To be able to test different decision choices systematically for an
index, the index needs to be broken down into its fundamental building
blocks to analyze the contribution and effect of each component. We call
this process of breaking the index construction into different steps the
index pipeline. Such decomposition of index components provides the
means to standardize index construction via a pipeline and offers
benefits for comparing among indexes and calculating index uncertainty.

@@

\hypertarget{background-to-index-usage-and-development}{%
\section{Background to index usage and
development}\label{background-to-index-usage-and-development}}

Indexes serve as critical tools to guide understanding and decisions
across natural and social sciences. In environmental science, climate
indexes are produces by major monitoring centres, such as the United
States Drought Monitor and National Oceanic and Atmospheric
Administration, to facilitate agricultural planning and early monitoring
on natural disaster. In economics, indexes provide insight into market
trends through combining a collection of representative items. In social
sciences, indexes are useful to measure social concepts such as human
development, gender equity, and university quality, which leads to
country ranking and enables cross-country comparison.

While the concept of combining variables into indexes finds widespread
application across various domains, indexes tend to develop separately
within each field. The OECD handbook (OECD, European Union, and Joint
Research Centre - European Commission 2008) provides a framework of
steps and recommendations. for composing socio-economic composite
indexes. The drought index handbook (Svoboda, Fuchs, et al. 2016),
instead, provides a practical guide outlining the advantage and
disadvantage of various drought indexes, as recommended by World
Meteorology Organization. Review papers in the literature summarise
different methodologies for constructing indexes from different
variables and statistical methods, for example, Zargar et al. (2011),
Hao and Singh (2015) Alahacoon and Edirisinghe (2022) for drought
indexes. In specific domains, attention are given to analyze the index
construction process, including the implications of the choices made
during the index construction (Jones and Andrey 2007) and uncertainty or
sensitivity analysis (Saisana, Saltelli, and Tarantola 2005; Tate 2012).

In software development, many tools encapsulate all the construction
steps into a single function to allow computing indexes with provided
data. This includes the \texttt{SPEI} package (Vicente-Serrano,
Beguería, and López-Moreno 2010) for two drought indexes, the
\texttt{gpindex} (Martin 2023) package for price indexes, and the
\texttt{fundiversity} package (Grenié and Gruson 2023) for functional
diversity indexes in ecology. The package \texttt{COINr} (Becker et al.
2022) deviates from this one-size-fit-all approach by following the
guidelines proposed in the OECD handbook to construct, analyze, and
visualize composite indexes.

@@

\hypertarget{tbl-notation}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0972}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2083}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1250}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2083}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3611}}@{}}
\caption{\label{tbl-notation}An notation overview of the input,
operation, and output of each pipeline module.}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Section
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Module
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Input
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Operation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Output
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Section
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Module
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Input
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Operation
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Output
\end{minipage} \\
\midrule()
\endhead
3.1 & Temporal processing & \(x_{sj}(t)\) & \(f[x_{sj}(t)]\) &
\(x^{\text{Temp}}_{sj}(t^\prime) \quad t^\prime \in D_{t^\prime}\) \\
3.2 & Spatial processing & \(x_{tj}(s)\) & \(g[x_{tj}(s)]\) &
\(x^{\text{Spat}}_{tj}(s^\prime) \quad s^\prime \in D_{s^\prime}\) \\
3.3 & Variable transformation & \(x_{j}(s; t)\) & \(T[x_j(s;t)]\) &
\(x^{\text{Trans}}_j(s;t)\) \\
3.4 & Scaling & \(x_j(s; t)\) & \([x_j(s;t) - \alpha]/\gamma\) &
\(x^{\text{Scale}}_j(s;t)\) \\
3.5 & Dimension reduction & \(\mathbf{x}(s;t)\) & \(h[\mathbf{x}(s;t)]\)
& \(\mathbf{y}(s;t) \quad \mathbf{y} \subseteq \mathbb{R}^d, d < q\) \\
3.6 & Distribution fit & \(x_j(s; t)\) & \(F[x_j(s;t)]\) &
\(p_j(s;t) \quad p(.) \in [0, 1]\) \\
3.7 & Normalising & \(x_j(s; t)\) & \(\Phi^{-1}[x_j(s; t)]\) &
\(z_j(s; t)\) \\
3.8 & Benchmarking & \(x_j(s; t)\) & \(u[x_j(s;t)]\) & \(b_j(s;t)\) \\
3.9 & Simplification & \(x_j(s; t)\) & \(v[x_j(s;t)]\) &
\(A_j(s;t) \in \{a_1, a_2, \cdots, a_j\}\) \\
\bottomrule()
\end{longtable}

@@

The temporal processing module takes as input argument a single variable
\(x_{sj}(t)\) at location \(s\) as a function of time. In this step the
original time series can be transformed or summarized into a new one via
time aggregation, the transformation is represented by the function
\(f\), \(x^{\text{Temp}}_{sj}(t^\prime) = f[x_{sj}(t)]\) where
\(t^\prime\) refers to the new temporal resolution after aggregation. An
example of temporal processing done in the computation of the
Standardized Precipitation Index (SPI) (McKee et al. 1993), consists of
summing the monthly precipitation series over a rolling time window of
size \(k\). That is also known as the time scale. For SPI, the choice of
the time scale \(k\) is used to control the accumulation period for the
water deficit, enabling the assessment of drought severity across
various types (meteorological, agricultural, and hydrological).

@@

Dimension reduction takes the multivariate information
\(\mathbf{x}(s;t)\), where
\(\mathbf{x} \subseteq \mathbb{R}^q,\; q\leq p\), as the input. It
summarises the high-dimensional information into a lower-dimension
representation \(\mathbf{y}(s;t)\), where \(y \subseteq \mathbb{R}^d\)
and \(d < q\), as the output. The transformation can be based on
domain-specific knowledge, originating from theories describing the
underlying physical processes, or guided by statistical methods. For
example, the Standardized Precipitation-Evapotranspiration Index (SPEI)
(Beguería and Vicente-Serrano 2017) calculates the difference \(D\)
between precipitation (\(P\)) and potential evapotranspiration
(\(\text{PET}\)), using a water balance model (\(D = P - \text{PET}\)).
This is the only step that differs from the Standardized Precipitation
Index (SPI).

@@

The R package \texttt{tidyindex} implements a proof-of-concept of the
index pipeline modules described in Section~\ref{sec-pipeline}. These
modules compute an index in a sequential manner, as shown below:

@@

TODO: increase font for variable names

\hypertarget{confidence-interval}{%
\subsection{Confidence interval}\label{confidence-interval}}

also the ABS one - could display some uncertainties

@@

This work is funded by a Commonwealth Scientific and Industrial Research
Organisation (CSIRO) Data61 Scholarship. The article is created using
Quarto {[}@{]} in R {[}@{]}. The source code for reproducing this paper
can be found at: https://github.com/huizezhang-sherry/paper-tidyindex.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-alahacoon_comprehensive_2022}{}}%
Alahacoon, Niranga, and Mahesh Edirisinghe. 2022. {``A Comprehensive
Assessment of Remote Sensing and Traditional Based Drought Monitoring
Indices at Global and Regional Scale.''} \emph{Geomatics, Natural
Hazards and Risk} 13 (December): 762--99.
\url{https://doi.org/10.1080/19475705.2022.2044394}.

\leavevmode\vadjust pre{\hypertarget{ref-COINr}{}}%
Becker, William, Giulio Caperna, Maria Del Sorbo, Hedvig Norlen, Eleni
Papadimitriou, and Michaela Saisana. 2022. {``COINr: An r Package for
Developing Composite Indicators.''} \emph{Journal of Open Source
Software} 7 (78): 4567. \url{https://doi.org/10.21105/joss.04567}.

\leavevmode\vadjust pre{\hypertarget{ref-SPEI}{}}%
Beguería, Santiago, and Sergio M. Vicente-Serrano. 2017. \emph{SPEI:
Calculation of the Standardised Precipitation-Evapotranspiration Index}.
\url{https://CRAN.R-project.org/package=SPEI}.

\leavevmode\vadjust pre{\hypertarget{ref-buja_elements_1988}{}}%
Buja, A, D Asimov, C Hurley, and JA McDonald. 1988. {``Elements of a
Viewing Pipeline for Data Analysis.''} In \emph{Dynamic Graphics for
Statistics}, 277--308. Wadsworth, Belmont.

\leavevmode\vadjust pre{\hypertarget{ref-fundiversity}{}}%
Grenié, Matthias, and Hugo Gruson. 2023. \emph{{fundiversity}: Easy
Computation of Functional Diversity Indices}.
\url{https://doi.org/10.5281/zenodo.4761754}.

\leavevmode\vadjust pre{\hypertarget{ref-hao_drought_2015}{}}%
Hao, Zengchao, and Vijay P. Singh. 2015. {``Drought Characterization
from a Multivariate Perspective: {A} Review.''} \emph{Journal of
Hydrology} 527 (August): 668--78.
\url{https://doi.org/10.1016/j.jhydrol.2015.05.031}.

\leavevmode\vadjust pre{\hypertarget{ref-jones_vulnerability_2007}{}}%
Jones, Brenda, and Jean Andrey. 2007. {``Vulnerability Index
Construction: Methodological Choices and Their Influence on Identifying
Vulnerable Neighbourhoods.''} \emph{International Journal of Emergency
Management} 4 (2): 269--95.
\url{https://doi.org/10.1504/IJEM.2007.013994}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-gpindex}{}}%
Martin, Steve. 2023. \emph{Gpindex: Generalized Price and Quantity
Indexes}. \url{https://CRAN.R-project.org/package=gpindex}.

\leavevmode\vadjust pre{\hypertarget{ref-mckee1993relationship}{}}%
McKee, Thomas B, Nolan J Doesken, John Kleist, et al. 1993. {``The
Relationship of Drought Frequency and Duration to Time Scales.''} In
\emph{Proceedings of the 8th Conference on Applied Climatology},
17:179--83. 22. Boston, MA, USA.

@@

\leavevmode\vadjust pre{\hypertarget{ref-uncertainty}{}}%
Saisana, M., A. Saltelli, and S. Tarantola. 2005. {``{Uncertainty and
Sensitivity Analysis Techniques as Tools for the Quality Assessment of
Composite Indicators}.''} \emph{Journal of the Royal Statistical Society
Series A: Statistics in Society} 168 (2): 307--23.
\url{https://doi.org/10.1111/j.1467-985X.2005.00350.x}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-svoboda2016handbook}{}}%
Svoboda, Mark, Brian Fuchs, et al. 2016. {``Handbook of Drought
Indicators and Indices.''} \emph{Drought and Water Crises: Integrating
Science, Management, and Policy}, 155--208.

\leavevmode\vadjust pre{\hypertarget{ref-tate_social_2012}{}}%
Tate, Eric. 2012. {``Social Vulnerability Indices: A Comparative
Assessment Using Uncertainty and Sensitivity Analysis.''} \emph{Natural
Hazards} 63 (2): 325--47.
\url{https://doi.org/10.1007/s11069-012-0152-2}.

\leavevmode\vadjust pre{\hypertarget{ref-spei}{}}%
Vicente-Serrano, Sergio M., Santiago Beguería, and Juan I. López-Moreno.
2010. {``A {Multiscalar} {Drought} {Index} {Sensitive} to {Global}
{Warming}: {The} {Standardized} {Precipitation} {Evapotranspiration}
{Index}.''} \emph{Journal of Climate} 23 (7): 1696--1718.
\url{https://journals.ametsoc.org/view/journals/clim/23/7/2009jcli2909.1.xml}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-zargar2011review}{}}%
Zargar, Amin, Rehan Sadiq, Bahman Naser, and Faisal I Khan. 2011. {``A
Review of Drought Indices.''} \emph{Environmental Reviews} 19 (NA):
333--49.
